{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Added plot for Legendre Polynomials

	\paragraph{Monomial Basis}
	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials. Let $f(t)$ be an entire function, e.g. a polynomial, the exponential function or a trigonometric function, then we can write the following.

@@

	Due to the chosen implementation for our simulation, we will limit our paper to the case of $\alpha = 0$. However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis in later parts of this paper.
	Collinearity problems arise since the monomials become more correlated to each other as their degree increases, which can result in numerically unstable calculations. This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities. It can also lead to undesirable behavior away from the point of evaluation of the monomials (cf. \cite{ramsay_functional_2005}).

@@

	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be a Hilberst-Shmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by

@@

	\paragraph{Orthogonal Polynomials to Solve Collinearity Problems of Monomial Basis}

@@

\newpage
\include{tables_simulation.tex}

@@

	\section{Affidavit}

>>>>

	\paragraph{Monomial Basis}
	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials. Let $f(t)$ be an entire function, e.g. a polynomial, the exponential function or a trigonometric function, then we can express it in the following form.

@@

	Due to the chosen implementation for our simulation, we will limit our paper to the case of $\alpha = 0$. However, a different choice of $\alpha$ could lead to improvements in performance of the monomial basis in later parts of this paper.
	As the monomials are not pariwise orthogonal, this basis is also prone to Collinearity problems, which can result in numerically unstable estimates. This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities. It can also lead to undesirable behavior away from the point of evaluation of the monomials (cf. \cite{ramsay_functional_2005}).

@@

	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be a Hilberst-Schmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by

@@

	\paragraph{Orthogonal Polynomials to Solve Collinearity Problems of Monomial Basis}
	To address the collinearity problems described earlier, one possible idea would be to use a system of pair-wise orthogonal polynomials as a basis instead of the monomial basis. One example is the system of Legendre polynomials which are orthogonal by construction and have the same closed span as the monomials. Due to their orthogonality the problems of collinearity in the regressor matrix are greatly reduced which could allow for larger numbers of basis functions in the basis expansion regression approach. The first eight Legendre polynomials are shown in Appendix section \ref{Basis_Plots}.

@@

	\begin{figure}[H]\label{Legendre_basis}
		\includegraphics[width = \textwidth]{../Graphics/Legendre_Plot.pdf}
		\caption{Legendre Polynomials of degree 0 to 7}
	\end{figure}

\include{tables_simulation.tex}

@@

	\section*{Affidavit}
